Data Exploration: IUCN and AquaMaps

### 2017-04-10 data_explore/data_explore.Rmd
bar chart now appears under quad plot

# ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 19.05, height = 7, units = 'cm', dpi = 600)

@@

# ggsave(plot = bar_spp_gp_quads_ex,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads_ex.png'),
       width = 19.05, height = 7, units = 'cm', dpi = 600)

write_csv(spp_gp_quadrants, file.path(dir_data, 'spp_gp_quads_ex.csv'))

>>>>

# ggsave(plot = barchart_spp_gp_quads,
       # filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       # width = 19.05, height = 7, units = 'cm', dpi = 600)

@@

# ggsave(plot = bar_spp_gp_quads_ex,
       # filename = file.path(dir_fig, 'barchart_spp_gp_quads_ex.png'),
       # width = 19.05, height = 7, units = 'cm', dpi = 600)

write_csv(spp_gp_quads_ex, file.path(dir_data, 'spp_gp_quads_ex.csv'))
